Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-03-20 text/paper2/ms.tex
data quality

\subsection{Precise distance measurements with missing proper motions}
The SMASH survey \citep{smashprop} will be completed by XXX, long before the final \gaia\, data release. Thus, we will soon have precise distance measurements for stars in the Sgr and Orphan streams, but poor proper motion constraints. [some comments on state of data for Sgr core, proper motions of] Here we study how well we can constrain the potential with our model given stars with missing data. We use the same observational uncertainties for the stars as mentioned in the previous experiment, but assume the proper motion's have not been measured.

>>>>

\subsection{Precise distance measurements with missing proper motions}
The SMASH survey \citep{smashprop} will be completed by XXX, long before the final \gaia\, data release. Thus, we will soon have precise distance measurements for stars in the Sgr and Orphan streams, but poor proper motion constraints. [some comments on state of data for Sgr core, proper motions of] Here we study how well we can constrain the potential with our model given stars with missing proper motions. We use the same observational uncertainties for the stars as mentioned in the previous experiment, but assume the proper motion's have not been measured.
